---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# senimuse

<!-- badges: start -->
[![R-CMD-check](https://github.com/farhanreynaldo/senimuse/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/farhanreynaldo/senimuse/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of senimuse is to provide an R interface to the museum API, allowing users to easily access and analyze artwork data from the collection. This package simplifies the process of retrieving information about artworks, artists, exhibitions and other museum resources for data analysis, visualization, and research purposes.

## Installation

You can install the development version of senimuse from GitHub with:

``` r
library(devtools)
install_github("farhanreynaldo/senimuse")
```

## Example

Below is an example of how to retrieve artwork information from a museum collection using senimuse:

```{r example}
library(senimuse)
get_artworks(4, fields = c("id", "title", "date_start", "date_end"))
```
