---
title: "introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction to senimuse

The `senimuse` package provides straightforward tools to access and search through museum collection data via their public APIs. It currently supports the Art Institute of Chicago (ARTIC) and Metropolitan Museum of Art (MET), allowing R users to incorporate cultural datasets into their research, education, or data visualization projects.

## Basic Usage

The package offers two main functions:

`get_artworks()` - Retrieve specific artwork(s) using object IDs
`search_artworks()` - Search museum collections by keyword
Let's explore how to use these functions with examples:

### Retrieving Specific Artworks

When you know the ID of the artwork you want to access, use `get_artworks()`:

```{r}
library(senimuse)

# Get data for a single artwork from Art Institute of Chicago (default museum)
artic_artwork <- get_artworks(4)
print(artic_artwork)

# Get a specific artwork from the Metropolitan Museum of Art
met_artwork <- get_artworks(436535, museum = "met")
print(met_artwork)
```

### Searching for Artworks

To discover artworks based on keywords, use `search_artworks()`:

```{r}
# Search for artworks related to "sunflowers" in ARTIC
sunflower_artworks <- search_artworks("sunflowers")
print(sunflower_artworks)

# Search for works by Monet in the Met collection
monet_artworks <- search_artworks("monet", museum = "met")
print(monet_artworks)
```

### Refining Results

Both functions allow you to specify which fields to return:

```{r}
# Get specific fields for multiple artworks
selected_fields <- get_artworks(
  c(27992, 28560), 
  museum = "artic",
  fields = c("title", "artist_display", "date_display")
)
print(selected_fields)

# Increase the number of search results
landscape_artworks <- search_artworks(
  "landscape", 
  museum = "met", 
  size = 25
)
```

## Working with Results

The functions return data in tibble (data frame) format, which integrates smoothly with tidyverse operations:

```{r}
library(dplyr)

# Filter for artworks from a specific period
impressionist_works <- search_artworks("impressionism", museum = "met") %>%
  filter(grepl("19th century", date_display))

# Count artworks by artist
artist_counts <- search_artworks("portrait", size = 30) %>%
  group_by(artist_display) %>%
  summarize(count = n()) %>%
  arrange(desc(count))
```

## Supported Museums

Currently, `senimuse` supports:
* Art Institute of Chicago ("artic")
* Metropolitan Museum of Art ("met")

The package standardizes column names across museum APIs for easier comparison and analysis.



